Aracna: An Open-Source Quadruped Platform for Evolutionary Robotics

### 2012-06-01 paper_aimsa/experimentalSetup.tex
word wrap, added fig
Added links to many references

hardware details, ...

Setup: The quadruped robot used was assembled from parts purchased online and parts printed by the Objet Connex 500 3-D Printing System. The robot actuation system consists of 5 AX-18+ Dynamixel servos and 4 AX-12+ Dynamixel servos: one inner joint with one AX-18+ servo and one outer joint with AX-12+servo in each of the four legs, and one AX-18+ servo at the center. To avoid the formerly reported AX-18+ servos are used in this robot because of their stronger actuation power than that of AX-12+. Each servo could be set to a position in the range [0, 1023] by using PyDynamixel library, corresponding to a physical range [-120, +120]. Also, to prevent collisions with the robot body, the control module filter out the commands to a safe range. This range was [-85, +60 ] for the inner leg servos, [-113 , +39 ] for the outer leg servos, and [-28 , +28] for the center hip servo. In the studies of this paper, tethered cables powered both the computer and the servos. It measures approximately 39.5 centimeters from leg to opposite leg in the crouch position showed in [pic].Our performance metric was the displacement over the evaluation period of 12 seconds for each. Same as Jason et al described in [xx], the displacement was measured using a Wii remote that was placed on the ceiling. Different from the original model described in [xx], the quadruped robot was equipped with a three-infrared-LED cluster on top rather than just one. The reason for this setup is that when fierce gaits were executed, the Wii remote loses tracking of the robot position due to the limited visible angle of a single LED.  These three LEDs were place tightly together to act as one signal emitter. Each LED was tilted outwards in order to maximize the visible range. [pic] A separate tracking server ran on the robot PC interacted with the Wii remote via bluetooth by using the CWiid library.  A corresponding client communicates with this server via a socket connection. Our fitness evaluation code talks with the Wii remote by using this client and updates the position from beginning to end during each run. The metric for evaluating gaits was the Euclidian distance the robot traveled during a 12-second run on flat surface. Previous work done in [xx] and [xx1(k)] suggested that extremely fierce are not viable in general. These gaits tend to either overburden the servos or flip the robot. Thus, RL\_POWER(?) were tested after carefully cropping out the extremely fierce gaits each time. (As described earlier, each leg has two joints, inner joint j1 and outer j2. The position of one leg is determined by the sum of the values of j1 and j2. Extremely fierce gaits usually have relatively small values of g. Thus cropping works by mapping the wild gaits onto the boundary of a triangular space over the two dimensional space of j1 and j2. [pic of j1 j2 space] [g = j1 + j2] caption

>>>>

The quadruped robot used was assembled from parts purchased online and
parts printed by the Objet Connex 500 3-D Printing System. The robot
actuation system consists of 5 AX-18+ Dynamixel servos and 4 AX-12+
Dynamixel servos: one inner joint with one AX-18+ servo and one outer
joint with AX-12+servo in each of the four legs, and one AX-18+ servo
at the center. To avoid the formerly reported AX-18+ servos are used
in this robot because of their stronger actuation power than that of
AX-12+. Each servo could be set to a position in the range [0, 1023]
by using PyDynamixel library, corresponding to a physical range [-120,
  +120]. Also, to prevent collisions with the robot body, the control
module filter out the commands to a safe range. This range was [-85,
  +60 ] for the inner leg servos, [-113 , +39 ] for the outer leg
servos, and [-28 , +28] for the center hip servo. In the studies of
this paper, tethered cables powered both the computer and the
servos. It measures approximately 39.5 centimeters from leg to
opposite leg in the crouch position showed in [pic].Our performance
metric was the displacement over the evaluation period of 12 seconds
for each. Same as \cite{yosinski2011evolving-robot-gaits}, the displacement was
measured using a Wii remote that was placed on the ceiling. Different
from the original model described in \cite{yosinski2011evolving-robot-gaits}, the quadruped robot was
equipped with a three-infrared-LED cluster on top rather than just
one. The reason for this setup is that when fierce gaits were
executed, the Wii remote loses tracking of the robot position due to
the limited visible angle of a single LED.  These three LEDs were
place tightly together to act as one signal emitter. Each LED was
tilted outwards in order to maximize the visible range. [pic] A
separate tracking server ran on the robot PC interacted with the Wii
remote via bluetooth by using the CWiid library.  A corresponding
client communicates with this server via a socket connection. Our
fitness evaluation code talks with the Wii remote by using this client
and updates the position from beginning to end during each run. The
metric for evaluating gaits was the Euclidian distance the robot
traveled during a 12-second run on flat surface. Previous work done in
\cite{yosinski2011evolving-robot-gaits} and \cite{clune2009evolving-coordinated-quadruped} suggested that extremely fierce gaits are not viable in
general. These gaits tend to either overburden the servos or flip the
robot. Thus, RL\_POWER(?) were tested after carefully cropping out the
extremely fierce gaits each time. (As described earlier, each leg has
two joints, inner joint j1 and outer j2. The position of one leg is
determined by the sum of the values of j1 and j2. Extremely fierce
gaits usually have relatively small values of g. Thus cropping works
by mapping the wild gaits onto the boundary of a triangular space over
the two dimensional space of j1 and j2. \figref{smartCrop}....

\figp{smartCrop}{1}{$g = j1 +  j2$ caption}

\figp{sixLegPositions}{1}{caption... the left two are allowed, middle
  two are on the red border line from \figref{smartCrop}, right two
  are disallowed.}

### 2012-06-01 paper_aimsa/introduction.tex
Added picture of quadratot with booties
Added links to many references

\figp{aracna_black_2}{.75}{Example figure...}

Various learning algorithms have been tested to be effective for
legged robots. Their studies tested the viability of applying RL
method to legged robot gaits learning. Competitive performance has
been verified on methods such as HyperNEAT (Yosinski et al, 2011) and
GA(Chernova et al, 2004) and other methods(Hornby et al., 2005; Zykov
et al., 2004; T´ellez et al., 2006; Valsalam and Miikkulainen,
2008). Despite the excellent performance of these algorithms, a major
part of achieving good performance relies in tuning the parameters for
the evolutionary algorithms(Kormushev et al, 2006). Here we present a
different way for learning gaits using RL(Hill climbing). In our
experiment, it turned out this method achieved competitive performance
with Problem Definition:The gait-learning problem is defined to find a
gait that maximizes some specific metric. Mathematically, we define a
gait as a function that specifies a vector of commanded motor
positions for a robot over time. Gaits without feedback --- also
called open-loop gaits --- can be defined as

>>>>

\figp{quadratotWhiteBooties}{.75}{Example figure...}

Various learning algorithms have been tested to be effective for
legged robots. Their studies tested the viability of applying RL
cite{yosinski2011evolvingmethod to legged robot gaits learning. Competitive performance has
been verified on methods such as HyperNEAT \cite{yosinski2011evolving-robot-gaits} and
GA \cite{chernova2004an-evolutionary-approach-to-gait} and other methods \cite{hornby2005autonomous-evolution-of-dynamic} \cite{zykov2004evolving-dynamic-gaits} \cite{tellez2006evolving-the-walking-behaviour} \cite{valsalam2008modular-neuroevolution-for-multilegged}. Despite the excellent performance of these algorithms, a major
part of achieving good performance relies in tuning the parameters for
the evolutionary algorithms \cite{kormushev2011bipedal-walking-energya}. Here we present a
different way for learning gaits using RL (Hill climbing). In our
experiment, it turned out this method achieved competitive performance
with Problem Definition:The gait-learning problem is defined to find a
gait that maximizes some specific metric. Mathematically, we define a
gait as a function that specifies a vector of commanded motor
positions for a robot over time. Gaits without feedback --- also
called open-loop gaits --- can be defined as

### 2012-06-01 paper_aimsa/results.tex
Added links to many references

A corresponding observation of this property is that the noisiness of
RL\_POWER is significantly lower than that of HyperNEAT. One reason of
this is that the when Expectation Maximization methodology is used,
explorations happened in the vicinity space of the highest ranked
patterns. Even some individual HyperNEAT gaits turned out very
effective, the average noisiness of HyperNEAT is very large. For
example, as found in [xx], the mean of HyperNEAT generation-champion’s
performance was XX body lengths/minute (+-XX SD), but it had a max of
38 and a min of 3. RL\_POWER, on the other hand, proved to be stable
and much less noisy throughout the entire experiment. The maximum SD
over all three runs is +- XX SD. This may also be due to a much larger
space of possibilities of HyperNEAT than the more heuristically guided
reinforcement learning.

>>>>

A corresponding observation of this property is that the noisiness of
RL\_POWER is significantly lower than that of HyperNEAT. One reason of
this is that the when Expectation Maximization methodology is used,
explorations happened in the vicinity space of the highest ranked
patterns. Even some individual HyperNEAT gaits turned out very
effective, the average noisiness of HyperNEAT is very large. For
example, as found in \cite{yosinski2011evolving-robot-gaits}, the mean of HyperNEAT generation-champion’s
performance was XX body lengths/minute (+-XX SD), but it had a max of
38 and a min of 3. RL\_POWER, on the other hand, proved to be stable
and much less noisy throughout the entire experiment. The maximum SD
over all three runs is +- XX SD. This may also be due to a much larger
space of possibilities of HyperNEAT than the more heuristically guided
reinforcement learning.
